Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-02-19 Journal1/Response (21-10-2019)/Response.tex

We add this response in subsection IV-A.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 8:} ``Also, interference is measured in a more detailed manner (maximum interference per UE) and hence when this relaxed (Guassian noise) the performance expected to slightly increase. Hence, some more detailed discussion on what has been assumed is needed. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise which is shown in Fig \ref{fig:pq}. We offer the sum of interference and the Gaussian quantization noise with $ I_{r,u(s,i)}^{k}$. Also, the Gaussian quantization noise is independent of interference and related to channel gain of UEs.

We add this response in subsection II-B.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!45}
\textbf{Reviewer 3} \\
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comments to the Author} ``The authors propose a resource allocation scheme for network slicing in an Open RAN scenario. They consider three network slice types namely eMBB, URLLC and mMTC and provide a solution for end-to-end slicing considering resource allocation over the RAN domain following the proposed ORAN architecture, as well as VNF allocation. In general, the paper is well written, however some parts need to be rephrased and restructured.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for careful and thorough reading of our manuscript and for
the thoughtful comments and constructive suggestions, which helped us to improve
the quality of this manuscript. We hope that the modifications that we have made to the manuscript, and the
responses that we have provided herein will alleviate the reviewer concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 1:} ``The paper presents an interesting solution and an extremely well formulated mathematical problem; however, the main contribution of the paper is hard to grasp. For instance, the introduction of the paper is very generic. There are a lot of concepts and methods explained, nonetheless not related to the proposed solution. The main issue lies in the structure of the work. The main contribution only appears at the end of page 2, where after an extensive reading the interest of the reader starts to vanish. I would definitely suggest a restructuring here. For instance, directly hint the main objectives and motivation of the work to prepare the reader for what is following. Moreover, the Related work could be a section of its own. In that way, the organization of the paper is clearer and easier to read.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Thank you for helping me to change my introduction.
I have changed the introduction of my paper.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 2:} ``Finally, a better distinction of the current proposal from the state-of-the-art is mandatory, otherwise it is hard to understand how the proposed algorithm differs from existing works in the literature which seem to provide solution to a similar problem.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
The purposes of this paper are twofold. First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC. Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing. Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system. 
In this paper, we want to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform. 
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
The novelty of this paper is to enhance the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing. We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 3:} ``Furthermore, while the math introduced in the paper is solid, it is also hard to follow for a reader if illustrations are not presented. It would be easier if a Figure is introduced for instance to explain equations from 3a -3d, where a lot of variables are presented. Especially, for the concepts of inter and intra slice isolation, which are very crucial. Following, that logic more elaboration especially with respect to inter slice isolation and why it needs to be considered in the equation, is important, as one could say that a careful scheduling has to definitely avoid distribution of the same resources within a slice to different users i.e., (orthogonality constraint).''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
I have add this part in the system model. 
Assume we have $K$ physical resource blocks (PRBs) in this system. Suppose each slice s consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs). Therefore, we have $\sum_s \bar{K}_s \leq K$.

Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
 r$. UEs in each slice interfere in two ways in the technique of network slicing: the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
Network Slicing methods significantly reduce inter-service interference.
There are some techniques to remove inter-slice interference. One of these techniques is to have two-time scale scheduling. The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out. Since there are limited resources, inter-service interference cannot be eliminated entirely. The other method is to allocate part of the RB of eMBB services to URLLC and mMTC  [2], [6], [34]. In this paper, we assume that the PRB scheduling is performed. Also, in subsection II-F1, we briefly study the PRB scheduling between slices.
\begin{figure}
  \centering 
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.35]{Interference.png}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Type of Interference Signal}
  \label{fig:intf}
\end{figure}
$I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.

 In this section, we have a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices [37].
We need to have an algorithm to remove the inter-slice interference before solving the problem \ref{problem}. Firstly, we should assign PRBs to slices, and in the second step, the assignment of PRBs of each slice to each UEs of a specific slice is performed. So, the assignment of PRB can be completed in two steps to remove inter-slice interference and isolate the slices. Firstly we assign PRBs to slices. Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses the proposed algorithm \ref{proAlg}.
Suppose, $\mathcal{R}_{{s}}^{min}$, and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
Firstly, we need to find the average PRB number used by UEs in each service. Since mMTC and URLLC transmit a short packet, each UE in mMTC and URLLC requires 1 PRB. So if slice s serves mMTC or URLLC services, with $U_s$ UEs, it requires $K_s = U_s \times 1$ PRBs. For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = Blog_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s. (eMBB slice)
So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$. $K_s^{min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.  
Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$. $K_s^{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system. Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRB in slice s (eMBB slice).
Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
The problem can be written as follow
\begin{subequations}\label{prob:prb}
\begin{alignat}{4}
\max\limits_{\boldsymbol{\bar{K_s}}} \quad &  \sum_{s=1}^{S}\delta_s K_s \ln(\bar{K_s}) \ \\
\text{subject to} \quad  & \sum_s{\bar{K_s}} \leq K
 \label{prb0} \\
& K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\
&  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3,\label{prb2}
\end{alignat}
\label{constraints}
\end{subequations}
We used logarithms to assign PRBs to all slices to make
them equally fair [37]. Equation (14b) illustrates that the
sum of PRBs of slices can not exceed the maximum number
of PRBs. Equation (14c), restrict the number of PRBs
of eMBB slices and (14d), limit the number of PRBs of
URLLC and mMTC slices By relaxing $\bar{K_s}$, the objective function and constraints become convex and can be solved using the Lagrangian function.

Also, I add a new subsection II-E-1 about PRB scheduling for this question.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 4:} ``Additionally, since the authors claim their novelty on the introduction of ORAN architecture, it becomes of utmost importance to consider concepts such as the creation of a slice, management of a slice and well as deletion, which bridge the mathematical framework to the practical one. For instance, how is a network slice created in the proposed work? How are the requirements of a slice fed to the algorithm? How is the monitoring of a slice performed?''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
This subsection aims to examine slice management, including creating, managing, and deleting slices. Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning [38]. 
\begin{itemize}
\item Preparation phase: The network slice instance (NSI) does not exist in the preparation phase. In this phase, operators plan to create an NSI, such as designing the NSI template, onboarding users, and preparing the environment. Also, the evaluation of requirements is performed in this step.
\item Commissioning phase: In the commissioning phase, the creation of the NSI is done. In this phase, the requirements are considered and allocated to the slice. 
\item Operation phase: During the Operation phase, NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated. As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
\item Decommissioning phase: A NSI that is decommissioned no longer exists after the decommissioning phase.
\end{itemize}

I add a new subsection II-G about Slice management for this question.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 5:} ``Finally, the authors propose an interesting solution, however in none of the results information with respect to the convergence time of the algorithm were presented. This becomes extremely crucial when considering the real deployment of such a solution. In that regard, some findings with regard to this aspect need to be definitely included in the work.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
It is shown in Fig. 11 and subsection III-C-1 and III-C-2.

### 2022-03-03 Journal1/paper3TNSM/pr.tex
Add paper

\textcolor{blue}{To achieve the desired level of QoS (quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks. There are several implementations of network slicing, including core slicing, RAN slicing, and both. 

@@

\textcolor{blue}{This paper considers various user equipments (UEs) requesting one of these types of services with different QoS. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}

\textcolor{blue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks. O-RAN was developed due to integrating virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both. With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly. The CRAN divides the radio remote head (RRH) and baseband unit (BBU) into two major parts. Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).}

\textcolor{blue}{O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.}

\textcolor{blue}{This paper aims to design a RAN slicing technology in O-RAN architecture. }
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

@@

\textcolor{blue}{This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC. As well as baseband resources, the optimal number of VNFs is also taken into account to reduce latency for URLLC services.}
\subsection{Related Literature}
The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity. Also, the allocation of power and physical resource blocks (PRB) is performed in the lower level.
In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).

@@

%All $K$ PRBs can be assigned to all UEs in each service. 
\textcolor{Sepia}{ Assume we have $K$ physical resource blocks (PRBs) in this system. Suppose each slice s consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs). Therefore, we have $\sum_s \bar{K}_s \leq K$.
}
In addition, there are $R$ multi-antenna O-RUs that are shared between slices. O-RU $r \in \{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data. Also $\mathcal{R} = \{ r \ | \ r\in 1,2,...,R \}$ depicts the set of O-RUs. Moreover, all O-RUs have access to all PRBs.

@@

\textcolor{Sepia}{Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
 r$. UEs in each slice interfere in two ways in the technique of network slicing: the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
Network Slicing methods significantly reduce inter-service interference.
There are some techniques to remove inter-slice interference. One of these techniques is to have two-time scale scheduling. The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out. Since there are limited resources, inter-service interference cannot be eliminated entirely. The other method is to allocate part of the RB of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.} In this paper, we assume that the PRB scheduling is performed. Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.
\begin{figure}
  \centering 
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.35]{Interference.png}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Type of Interference Signal}
  \label{fig:intf}
\end{figure}
\textcolor{teal}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow}
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
\textcolor{Sepia}{Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.}

\textcolor{NavyBlue}{Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise. The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.}
\textcolor{teal}{To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as

@@

\textcolor{teal}{where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$. Also, ${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.

@@

\textcolor{olive}{The processing delay can be considered an M/M/1; since the number of arrival packets in the system is enormous, and the packets are independent. Moreover, the impact of a single packet on the system's performance is minimal. Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process. The system's clock is constant, and the size of the tasks is not fixed. So, we suppose that service times are exponentially distributed \cite{QS}. In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services, not between UEs of one service. Because we assumed that the UEs of a service have the same priority, their sent packets also have an equal priority. Also, the services are isolated, and this priority does not invalidate the queue assumption. Furthermore, one service's priority over another can be higher, affecting the whole optimization and not queue formulation since the UEs in each service have the same priority, and each service has its processing delay independent of other services.} 
\subsection{VNF Power}
%{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.} 
Assume the power consumption of each VNF in each logical node (the O-DU, the O-CU, and the UPF) in the slice s, is depicted as $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.

@@

\textcolor{gray}{A significant issue facing the industry is reducing energy consumption. Data centers are one of the most energy-consuming. As a result, restrictions are placed on data centers' energy, including virtual machines (VMs). So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers. So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).}

@@

\text{subject to} \quad  &  P_r \leq P^{max}_{r} \quad \forall r

@@

&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{min} \quad \forall s, \label{c13} \\

>>>>

\textcolor{MidnightBlue}{To achieve the desired level of QoS (quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks. There are several implementations of network slicing, including core slicing, RAN slicing, and both. 

@@

\textcolor{MidnightBlue}{This paper considers various user equipments (UEs) requesting one of these types of services with different QoS. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}

\textcolor{MidnightBlue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks. O-RAN was developed due to integrating virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both. With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly. The CRAN divides the radio remote head (RRH) and baseband unit (BBU) into two major parts. Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).}

\textcolor{MidnightBlue}{O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.}

\textcolor{MidnightBlue}{This paper aims to design a RAN slicing technology in O-RAN architecture. }
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

@@

\textcolor{MidnightBlue}{This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC. As well as baseband resources, the optimal number of VNFs is also taken into account to reduce latency for URLLC services.}
\subsection{Related Literature}
The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity. Also, the allocation of power and physical resource blocks (PRB) is performed in the lower level.
In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).

@@

%All $K$ PRBs can be assigned to all UEs in each service. 
\textcolor{MidnightBlue}{ Assume we have $K$ physical resource blocks (PRBs) in this system. Suppose each slice s consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs). Therefore, we have $\sum_s \bar{K}_s \leq K$.
}
In addition, there are $R$ multi-antenna O-RUs that are shared between slices. O-RU $r \in \{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data. Also $\mathcal{R} = \{ r \ | \ r\in 1,2,...,R \}$ depicts the set of O-RUs. Moreover, all O-RUs have access to all PRBs.

@@

\textcolor{MidnightBlue}{Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
 r$. UEs in each slice interfere in two ways in the technique of network slicing: the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
Network Slicing methods significantly reduce inter-service interference.
There are some techniques to remove inter-slice interference. One of these techniques is to have two-time scale scheduling. The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out. Since there are limited resources, inter-service interference cannot be eliminated entirely. The other method is to allocate part of the RB of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.} In this paper, we assume that the PRB scheduling is performed. Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.
\begin{figure}
  \centering 
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.35]{Interference.png}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Type of Interference Signal}
  \label{fig:intf}
\end{figure}
\textcolor{MidnightBlue}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow}
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
\textcolor{MidnightBlue}{Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.}

\textcolor{MidnightBlue}{Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise. The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.}
\textcolor{MidnightBlue}{To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as

@@

\textcolor{MidnightBlue}{where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$. Also, ${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.

@@

\textcolor{MidnightBlue}{The processing delay can be considered an M/M/1; since the number of arrival packets in the system is enormous, and the packets are independent. Moreover, the impact of a single packet on the system's performance is minimal. Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process. The system's clock is constant, and the size of the tasks is not fixed. So, we suppose that service times are exponentially distributed \cite{QS}. In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services, not between UEs of one service. Because we assumed that the UEs of a service have the same priority, their sent packets also have an equal priority. Also, the services are isolated, and this priority does not invalidate the queue assumption. Furthermore, one service's priority over another can be higher, affecting the whole optimization and not queue formulation since the UEs in each service have the same priority, and each service has its processing delay independent of other services.} 
\subsection{VNF Power}
%{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.} 
Assume the power consumption of each VNF in each logical node (the O-DU, the O-CU, and the UPF) in the slice s, is depicted as $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.

@@

\textcolor{MidnightBlue}{A significant issue facing the industry is reducing energy consumption. Data centers are one of the most energy-consuming. As a result, restrictions are placed on data centers' energy, including virtual machines (VMs). So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers. So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^\text{max}$).}

@@

\text{subject to} \quad  &  P_r \leq P^\text{max}_{r} \quad \forall r

@@

&p_{r,u(s,i)}^{k}  \leq P_{s}^\text{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{\min} \quad \forall s, \label{c13} \\
